### 2020-05-06 writeup/transfer.tex

\section{Variance Reduction from Information Transfer}\label{sec_denoise}

In this part, we consider the case of two tasks to show  establish the intuition that adding more data helps in multi-task learning by reducing the variance of the estimator.
We achieve this through tight generalization bounds obtained from random matrix theory.
For the case of two tasks, we identify three factors that determine the type of transfer between tasks: model distance, covariate shift matrix, and data ratio.

Recall that the test error of $\hat{\beta}_{t}^{\MTL}$ consists of two parts
\begin{align}
	\te(\hat{\beta}_t^{\MTL}) = \hat{w}^2 \bignorm{\Sigma_2^{1/2} (\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_s - \hat{w}\beta_t)}^2 + \sigma^2\cdot \bigtr{(\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}. \label{eq_te_model_shift}
\end{align}
It is not hard to show that the variance of $\hat{\beta}_t^{\MTL}$ is reduced compared to $\hat{\beta}_t^{\STL}$ (following the argument of Proposition \ref{prop_monotone}), i.e.
\[ \sigma^2\cdot \bigtr{(\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \le \sigma^2\cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}. \]
Because of model shift however, i.e. $\beta_s \neq \beta_t$.
We can no longer guarantee that $\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL})$.
The main result of this part show deterministic conditions under which we get positive or negative transfer.
And the conditions depend only on the covariate shift matrix $M$, the difference of the task models, and the number of per-task data points.
In order to characterize $\te(\hat{\beta}_t^{\MTL})$ and $\te(\hat{\beta}_t^{\STL})$, the technical crux of our approach relies on deriving the limit of the trace of matrix inverse in the high-dimensional setting.
To illustrate the idea, we observe that by using Lemma \ref{lem_minv}, we have that
\[ \te(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{n_2 - p}\bigtr{\Sigma_2^{-1}}. \]
We shall also derive the limit of $\te(\hat{\beta}_t^{\MTL})$.
\todo{write a brief technical overview}

%In this case, $\beta_s$ and $\beta_t$ are different.
%, or implicitly add a regularization on $B$.
%\todo{We focus on the former case in this section.}
%, we consider the case when $r=1$ since there are only two tasks.
%We begin by considering the simplified equation \eqref{eq_mtl_basic} to solve for the target task.
%This is equivalent to setting $W_i = 1$ for the two tasks in equation \eqref{eq_mtl}.
%The result of this simplified setting will set up the ground for solving equation \eqref{eq_mtl} when we also optimize $W_1$ and $W_2$.
%By putting the two tasks together, we get
%\begin{align*}
%	\hat{\beta}_{s,t} &= (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (X_1^{\top}Y_1 + X_2^{\top}Y_2) \\
%	&= (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \bigbrace{(X_1^{\top}X_1\beta_s + X_2^{\top}X_2\beta_t) + (X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)} \\
%	&= \beta_t + (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\bigbrace{X_1^{\top}X_1(\beta_s - \beta_t) + (X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)}
%\end{align*}
%Hence
%\begin{align}
%	\err(\hat{\beta}_{s,t})
%	&= \bignorm{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}^2
%	+ \sigma^2 \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}, \text{ and} \\
%	\te(\hat{\beta}_{s,t})
%	&= \bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}^2 + \sigma^2\cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \label{eq_te_model_shift}
%\end{align}

\begin{algorithm}[!t]
	\caption{Comparing the test error of MTL, TL and STL estimators}
	\begin{algorithmic}[1]
		\Input Two regression tasks $(X_1, Y_2)$, $(X_2, Y_2)$.
		\Param Shared body $B$, task-specific prediction heads $W_1, W_2$.
		\State Training the shared body $B$.
		\State Optimizing the task heads on the validation set

		\begin{itemize}
			\item Jointly optimizing both tasks: $\hat{\beta}_t^{\MTL}$
			\item Optimizing the target task: $\hat{\beta}_t^{\TL}$
			\item Single-task training baseline: $\hat{\beta}_t^{\STL}$
		\end{itemize}
		\State Problem statement: Provide conditions to compare the test error of the three estimators on the target task, $\te(\hat{\beta}_t^{\MTL})$, $\te(\hat{\beta}_t^{\STL})$ and $\te(\hat{\beta}_t^{\TL})$.
	\end{algorithmic}
\end{algorithm}

Let ${M} = \hat{w} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix. Denote by ${\lambda}_1\ge {\lambda}_2 \ge \dots \ge {\lambda}_p$ the singular values of ${M}^{\top}{M}$. Let $(a_1, a_2)$ be the solutions to the following system of equations
	\be
		 a_1 + a_2 = 1- \frac{p}{n_1 + n_2},~ a_1 + \sum_{i=1}^p \frac{a_1}{(n_1 + n_2)(a_1 + a_2/ \lambda_i^2)} = \frac{n_1}{n_1 + n_2}.\label{eq_a2} \\
		 \ee
		 After obtaining $(a_1,a_2)$, we can solve the following linear equations to get $(a_3,a_4)$:
\begin{gather}
		\left(\frac{n_2}{a_2^2}- \sum_{i=1}^p \frac{1}{ (a_2 + \lambda_i^2a_1)^2  }\right) a_3 -  \left(\sum_{i=1}^p \frac{  \lambda_i^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right)a_4
		= \sum_{i=1}^p \frac{1 }{ (  a_2 + \lambda_i^2a_1)^2  }, \label{eq_a3} \\
		\left(\frac{n_1}{a_1^2} -  \sum_{i=1}^p \frac{\lambda_i^4   }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_4 -\left(\sum_{i=1}^p \frac{\lambda_i^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_3
		= \sum_{i=1}^p \frac{\lambda_i^2 }{  (a_2 + \lambda_i^2a_1)^2  }. \label{eq_a4}
	\end{gather}
Then we introduce the following matrix
$$Z = \frac{n_1^2}{(n_1 + n_2)^2}\cdot{M} \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{(a_2 + a_1 {M}^{\top}{M})^2} {M}^{\top},$$
which can be regarded as the asymptotic limit of $\hat w \Sigma_2^{1/2} (\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1^{1/2}$. Finally we introduce 
$$\delta:=\left[\frac{n_1 \lambda_1}{(\sqrt{n_1}-\sqrt{p})^2\lambda_p  +  (\sqrt{n_2}-\sqrt{p})^2}\right]^2\cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2.$$
{\cor may be able to get a better bound, but the statement will be long}

We now state our main result for two tasks with both covariate and model shift in the following theorem.

\begin{theorem}\label{thm_model_shift}
	Let $n_1, n_2$ be the number of data points for the source, target task, respectively.
	Let $\hat{w}$ denote the optimal solution for the ratio $w_1/w_2$ in equation \eqref{eq_val_mtl}.
	%Let ${M} = \hat{w} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
	%Denote by ${\lambda}_1, {\lambda}_2, \dots, {\lambda}_p$ the singular values of ${M}^{\top}{M}$.
	The information transfer is solely determined by two deterministic quantities $\Delta_{\beta}$ and $\Delta_{\vari}$, which show the change of model shift bias and variace, respectively.
	With high probability we have
	\begin{align}
	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \ge \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta \label{upper}\\
		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \le -2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta, \label{lower}
	\end{align}
	where 
	\begin{align*} %\bigtr{{\Sigma_2^{-1}}}
		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{p}{n_2 - p} -  \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top}M + a_2\id)^{-1}} } \\
		\Delta_{\beta} &\define (\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2} Z \Sigma_1^{1/2} (\beta_s - \hat{w}\beta_t).
	\end{align*}
%	{\color{blue}To write the bounds in the form \eqref{upper} and \eqref{lower}, we have to define $\wh w$ as the minimizer of
%	$$\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}}+ \Delta_\beta(w).$$
%	Otherwise, the two bounds has to be written into the form
%	\begin{align*}
%	{\sigma^2}\frac{p}{n_2 - p}\ge \min_w \left\{\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}} + \Delta_\beta(w)+ \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta(w)\right\},
%	\end{align*}
%	and
%	\begin{align*}
%	{\sigma^2}\frac{p}{n_2 - p}\le \min_w \left\{\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}}+ \Delta_\beta(w) - 2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta(w)\right\}.
%	\end{align*}
%	} 
\end{theorem}

%	We have the following conditions that guarantee the type of transfer we can get under model shift.
%	\begin{itemize}

%		\item {\bf Negative transfer:} we have $\te(\hat{\beta}_{s,t}) \ge \te(\hat{\beta}_t)$ when
%			\begin{align}
%				\Delta_{\vari} \le \bigbrace{1 - 4\sqrt{\frac{p}{n_1}} - \frac{2p}{n_1}} {\Delta_{\beta}}
%			\end{align}
%	\end{itemize}
%	\begin{align}
%		{\Delta_{\vari}} \ge \bigbrace{1 + \sqrt{\frac{p}{n_1}}}^2 {\Delta_{\beta}},
%\label{eq_model_shift_pos}
%	\end{align}
%	where
%{\cob
%We have that
%	\begin{align*}
%		&~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}} \\
%		&\le ~ \Delta_\beta^{1/2}+ \left\|M\frac{(1 + a_3)\id + a_4 M^{\top}M}{(a_1 + a_2 M^{\top}M)} M^{\top}\right\|_{op}^{1/2} \|\Sigma_1^{1/2} (\beta_s - \beta_t)\|_2 \left( 2\sqrt{\frac{p} {n_1}} + \frac{p}{n_1}\right),\\
%		\end{align*}
%		and
%	\begin{align*}
%		&~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}} \\
%		&\ge ~ \Delta_\beta^{1/2}- \left\|M\frac{(1 + a_3)\id + a_4 M^{\top}M}{(a_1 + a_2 M^{\top}M)} M^{\top}\right\|_{op}^{1/2} \|\Sigma_1^{1/2} (\beta_s - \beta_t)\|_2 \left( 2\sqrt{\frac{p} {n_1}} + \frac{p}{n_1}\right),
%	\end{align*}
%	In the case where the entries of $\beta_s-\beta_t$ are i.i.d. random variables and $\Sigma_1=\id$, we have
%\begin{align*}
%		& \Delta_\beta\left( 1-\sqrt{\frac{p}{n_1}}\right)^4 \le ~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}}^2 \le ~
%\Delta_\beta\left( 1+\sqrt{\frac{p}{n_1}}\right)^4.
%		\end{align*}
%	}

Theorem \ref{thm_model_shift} shows upper and lower bounds that guarantee positive transfer, which is determined by the change of variance $\Delta_{\vari}$ and a certain model shift bias parameter $\Delta_{\beta}$ determined by the covariate shift matrix and the model shift.
The bounds get tighter and tighter as $n_1 / p$ increases.
%\paragraph{Negative transfer: the Limit caused by model shifts.}
%Next we describe lower bounds that guarantee negative transfer to complement Theorem \ref{thm_model_shift}.
%\begin{theorem}[Negative transfer under model shift]\label{thm_model_shift_neg}
%	In the setting of Theorem \ref{thm_model_shift}, we have $\te(\hat{\beta}_{s,t}) \ge
%\te(\hat{\beta}_t)$ when
%	\begin{align*}
%		\Delta_{\vari} \le \bigbrace{1 - 4\sqrt{\frac{p}{n_1}} - \frac{2p}{n_1}} {\Delta_{\beta}}
%	\end{align*}
%	In the special case that $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$ and $\Sigma_1 = \id$, we can get a tighter lower bound that guarantees negative transfer when
%\begin{align}
%	\Delta_{\vari} \le \bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}.\label{eq_model_shift_neg}
%\end{align}
%
%\end{theorem}

%From Lemma \ref{lem_cov_shift}, we know that
%\[ \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} = \frac{1}{n_1 + n_2}\cdot \bigtr{ \bigbrace{a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id}^{-1}}, \]
%where $a_1, a_2$ are specified in Theorem \ref{thm_cov_shift}.
%Hence the variance part is reduced by the following amount
%\begin{align}
%	\Delta_{\vari} \define \sigma^2 \cdot \bigbrace{\frac{p}{n_2 - p} - \frac{1}{n_1 + n_2} \bigtr{\bigbrace{a_1 M^{\top}M + a_2\id}^{-1}}}
%\end{align}
%It remains to consider the increment from the first term in $\te(\hat{\beta}_{s,t})$, which is bounded using the following lemma.
%We are now interested in the following quantity

%\todo{For technical reasons, we will consider the test error.}
%\section{Effects of Model Distance, Covariate Shift, and Data Ratio on Information Transfer}\label{sec_insight}
\subsection{Effect of Model Distance on Positive versus Negative Transfer}

@@

\subsection{Extension to Many Tasks of the Same Covariates}

In this section we consider the setting with $k$ many that have the same covariates.
Since every task has the same number of data points as well as the same covariance, the only differences between different tasks are their models $\set{\beta_i}_{i=1}^k$.
For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.

Concretely we will consider the following problem.
\begin{align}
	f(B; W_1, \dots, W_k) = \sum_{i=1}^k \bignorm{X B W_i - Y_i}^2. \label{eq_mtl_same_cov}
\end{align}
By fixing $W_1, W_2, \dots, W_k$, we can derive a closed form solution for $B$ as
\begin{align*}
	\hat{B}(W_1, \dots, W_k) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^k Y_i W_i^{\top}} (Z Z^{\top})^{-1} \\
	&= \sum_{i=1}^k \bigbrace{\beta_i W_i^{\top}} (ZZ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^k \varepsilon_i W_i^{\top}} (ZZ^{\top})^{-1}
\end{align*}
where we denote $Z\in\real^{r\times k}$ as the $k$ vectors $W_1, W_2, \dots, W_k$ stacked together.
%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
Similar to Section \ref{sec_setup}, we consider minimizing the validation loss over $W_1, W_2, \dots, W_k$ provided with $\hat{B}$.

\paragraph{Jointly minimizing over all tasks.}
Denote by $\varepsilon(W) = \sum_{i=1}^k \varepsilon_i W_i^{\top}$.
We shall decompose the validation loss $\val(\hat{B}; W_1, \dots, W_k)$ into two parts.
The first part is the model shift bias, which is equal to
\begin{align*}
	\sum_{j=1}^k \bigbrace{\bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k(\beta_i W_i^{\top}) (ZZ^{\top})^{-1} W_j - \beta_j}}^2}
\end{align*}
The second part is the variance, which is equal to
\begin{align*}
	& \sum_{j=1}^k \exarg{\varepsilon_i, \forall i}{\bigbrace{\bigbrace{\sum_{i=1}^k \varepsilon_i W_i^{\top}} (ZZ^{\top})^{-1} W_j}^2} \cdot {\bigtr{\Sigma(X^{\top}X)^{-1}}} \\
	=& \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
\end{align*}
Therefore we shall focus on the minimizer for the model shift bias since the variance part does not depend the weights.
Let us denote $Q\in\real^{k\times k}$ where the $(i,j)$-th entry is equal to $W_i^{\top} (ZZ^{\top})^{-1} W_j$, for any $1\le i, j\le k$.
Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
We can now write the validation loss succinctly as follows.
\begin{align*}
	\val(\hat{B}; W_1, \dots, W_k) = \sum_{j=1}^k \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} Q - \beta_j}}^2 + \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}
\end{align*}
From the above we can solve for $Q$ optimally as \todo{this}.

\paragraph{Minimizing over the target task alone.}
If we only minimize over the the validation loss for the target task, we shall get the following.
\begin{align*}
	\val_j(\hat{B} W_j) = \bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k W_i^{\top} (ZZ^{\top})^{-1}W_j \beta_i - \beta_j}}^2
	+ \sigma^2 \cdot W_j^{\top} (ZZ^{\top})^{-1} W_j \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
\end{align*}

From the above we can obtain three conceptual insights that are consistent with Section \ref{sec_denoise} and \ref{sec_insight}.
\begin{itemize}
	\item The de-noising effect of multi-task learning.
	\item Multi-task training vs single-task training can be either positive or negative.
	\item Transfer learning is better than the other two. And the improvement over multi-task training increases as the model distances become larger.
\end{itemize}

\section{Effect of Covariate Shift and Data Ratio on Transfer Rate}

@@

% \begin{proposition}[Transfer rate without model shift] 
%	Suppose $\beta_s = \beta_t$ with i.i.d. entries of mean zero and variance $d^2$. Then we have that the optimal ratio for $W_1/W_2$ in equation \eqref{eq_te_mtl} satisfies 
%	$$1\le \hat{w} \le w_0:=1 + \frac{\sigma^2  \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}} }{\left\|( M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2},$$ 
%	where $\|\Sigma_1\|_{\min}$ is the smallest singular value of $\Sigma_1$. Note that $w_0$ is very close to $1$ up to a small error of order $n_1^{-1}$.
%\end{proposition}
\begin{proof}
We abbreviate $\val(w_2\hat{B}(w)):=\val(w)$. We first notice that $\val (w) < \val (1)$ for all $0\le w < 1$. Thus we have $\hat w\ge 1$. It suffices to consider the case with $w> 1$. Under the assumption on $\beta_s$ and $\beta_t$, we can write
\begin{align}
	\val(w) =&~  \left( 1-\frac1w\right)^2 \left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 \nonumber \\
			&~ + \frac{\sigma^2}{w^2} \cdot \bigtr{( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} }. \nonumber
\end{align}
Since 
$$\left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 = \tr \left[ ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-2}M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t\beta_t^\top \Sigma_1^{1/2}Z_1^{\top} Z_1  M\right]$$
is increasing with respect to $w$, then the derivative of $\val(w)$ can be bounded from below as
\begin{align*}
\val'(w) \ge &~ 2\frac{w-1}{w^3} \left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2   \\
			&~ - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(M^\top Z_1^{\top}Z_1 M +w^{-2}  Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top}Z_1 M (M^\top Z_1^{\top}Z_1 M + w^{-2} Z_2^{\top}Z_2)^{-1}} \\
\ge &~ 2\frac{w-1}{w^3} \left\|( M^\top Z_1^{\top}Z_1 M +  Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2   - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}}. 
			%\\ =& ~ 2\frac{d^2}{w^3} \tr\left[( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2}\id \right] Z_1 M ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1}\right]  .
\end{align*}
%We can write $\id = P+ P_{\perp}$, where $P$ denotes the projection onto the subspace spanned by the columns of $Z_1$ and $P_{\perp}$ denotes the projection onto its orthogonal complement. Together with $P\preceq (\sqrt{n_1}-\sqrt{p})^{-2} Z_1 Z_1^\top$, we get
%\begin{align*}
%M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2}\id \right] Z_1 M  &\succeq M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2(\sqrt{n_1}-\sqrt{p})^{2}} Z_1 Z_1^\top \right] Z_1 M  \\
%&= M^\top Z_1^{\top}Z_1  \left[\left( w-1\right) \Sigma_1  - \frac{\sigma^2}{d^2(\sqrt{n_1}-\sqrt{p})^{2}} \right] Z_1^\top Z_1 M .
%\end{align*}
Hence $\val'(w)\ge 0$ if $w\ge w_0$, i.e. $\val(w)$ is an increasing function on $[1+w_0,\infty]$. Thus we get $\hat w$ is between $[1,w_0]$. 
\end{proof}

>>>>

\section{Illustrative Examples}

\subsection{Effect of Model Distance on Positive versus Negative Transfer}

@@

\subsection{Effect of Covariate Shift and Data Ratio on Transfer Rate}

@@

\begin{proof}
We abbreviate $\val(w_2\hat{B}(w)):=\val(w)$. We first notice that $\val (w) < \val (1)$ for all $0\le w < 1$. Thus we have $\hat w\ge 1$. It suffices to consider the case with $w> 1$. Under the assumption on $\beta_s$ and $\beta_t$, we can write
\begin{align}
	\val(w) =&~  \left( 1-\frac1w\right)^2 \left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 \nonumber \\
			&~ + \frac{\sigma^2}{w^2} \cdot \bigtr{( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} }. \nonumber
\end{align}
Since
$$\left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 = \tr \left[ ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-2}M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t\beta_t^\top \Sigma_1^{1/2}Z_1^{\top} Z_1  M\right]$$
is increasing with respect to $w$, then the derivative of $\val(w)$ can be bounded from below as
\begin{align*}
\val'(w) \ge &~ 2\frac{w-1}{w^3} \left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2   \\
			&~ - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(M^\top Z_1^{\top}Z_1 M +w^{-2}  Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top}Z_1 M (M^\top Z_1^{\top}Z_1 M + w^{-2} Z_2^{\top}Z_2)^{-1}} \\
\ge &~ 2\frac{w-1}{w^3} \left\|( M^\top Z_1^{\top}Z_1 M +  Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2   - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}}. 
			%\\ =& ~ 2\frac{d^2}{w^3} \tr\left[( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2}\id \right] Z_1 M ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1}\right]  .
\end{align*}
Hence $\val'(w)\ge 0$ if $w\ge w_0$, i.e. $\val(w)$ is an increasing function on $[1+w_0,\infty]$. Thus we get $\hat w$ is between $[1,w_0]$.
\end{proof}
